Risk Perceptions for Wearable Devices

### 2015-04-16 tex-inputs/methodology.tex
Minor grammatical changes

\section{Methodology}
To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market. At the time of this study (August 2014) the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns;
%~\cite{6_fitbit_2014, 7_time_2014}
the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; %~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}
and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks such as search, reading emails, etc. %~\cite{11_wikipedia_2015, 12_turi_2014}. 
These devices' capabilities and requested permissions as inspiration to develop a list of possible security and privacy risks that users will encounter in use.

@@

Since this device is basis for many of our survey questions, we ensure that participants had understood this device's capabilities by asking them two multiple-choice comprehension questions about the device's. We filter out responses from participants who could not answer these questions.

\subsubsection{Wearable Scenarios}
We present scenarios involving data captured by the Cubetastic3000 and ask participants to rate how upset they would be if a particular type of data (e.g., video, audio, name, etc.) were shared without permission with a particular data recipient (see Figure \ref{fig:prompt}). Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}. Questions were of the form:

@@

We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>): %\\[-.8cm]

@@

\begin{quotation}
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?
\item How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?
\item How would you feel if an app on your <device> un-muted a phone call without asking you first?
\item How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?
\item How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
\end{enumerate}
\end{quotation}

@@

\subsubsection{Risk and Benefit Assessment}
In addition to investigating reactions to particular scenarios, we examine broad perceptions of new technologies and how those compared to perceptions of other understood technologies. We model this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society. We ask participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.  These technologies are chosen to span varying levels of risks and benefits.

Our goal was to ask about familiar technologies such as the Internet, general and specific wearable artifacts, and a range of new capabilities. To do this, we ask participants to evaluate one of 20 technologies relevant to wearables along 4 previously studied technologies. The 20 technologies are: Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.

>>>>

\section{Methodology}
To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market. At the time of this study (August 2014) the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns;
%~\cite{6_fitbit_2014, 7_time_2014}
the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; %~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}
and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks such as search, reading emails, etc. %~\cite{11_wikipedia_2015, 12_turi_2014}. 
These devices' capabilities and requested permissions were our inspiration to develop a list of possible security and privacy risks that users will encounter.

@@

Since this device is the basis for many of our questions, we ensured that participants had understood its capabilities by asking them two multiple-choice comprehension questions. We filtered out responses from participants who could not answer these questions.

\subsubsection{Wearable Scenarios}
We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., video, audio, name, etc.) was shared without permission with a particular data recipient (see Figure \ref{fig:prompt}). Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}. Questions were of the form:

@@

We combined 72 data types (<data>) with 4 data recipients (<recipient>) to form an initial pool of 288 questions: %\\[-.8cm]

@@

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?}
\item {\it How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?}
\item {\it How would you feel if an app on your <device> un-muted a phone call without asking you first?}
\item {\it How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?}
\item {\it How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
\end{enumerate}

@@

\subsubsection{Risk and Benefit Assessment}
In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies. We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society. We ask participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.  These technologies were chosen to span varying levels of risks and benefits.

Our goal was to ask about familiar technologies such as the Internet, general and specific wearable artifacts, and a range of new capabilities. To do this, we asked participants to evaluate one of 20 technologies relevant to wearables along 4 previously studied technologies. The 20 technologies were: Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.
